Population structure and phenotypic variation of \emph{Sclerotinia sclerotiorum} from dry bean in the United States

### 2017-09-19 doc/manuscript/manuscript.tex
run with docker container

\begin{figure}
\centering
\includegraphics[width=1.00000\textwidth]{../../results/figures/publication/mcg-subgraph-with-context.pdf}
\caption{Associations between Mycelial Compatibility Groups and
Multilocus Haplotypes. \textbf{A)} Barplot of Mycelial Compatibility
Group (MCG) abundance in descending order. Singletons (46) were
truncated, leaving 41 MCGs. White bars represent sample counts and grey
bars represent counts of unique multilocus haplotypes (MLH). The
transparency of the bars represent the evenness of the distribution of
the MLHs within a given MCG. A dashed box surrounds the eight most
common MCGs representing \textgreater{}~51\% of the data. \textbf{B)}
Full graph-representation of the relationship between MCGs (open
circles) and MLHs (filled circles). Details in Fig. \ref{fullgraph}.
\textbf{C)} A subset of \textbf{B} representing the 8 most common MCGs
and their associated MLHs (dashed box in \textbf{A}). Filled nodes
(circles) represent MLHs and open nodes represent MCGs. Node area scaled
to the number of samples represented (range: 1--73). Numbers inside
nodes are the MLH/MCG label (if n \textgreater{} 1). Edges (arrows)
point from MLH to MCG where the weight (thickness) of the edge
represents the number of shared isolates (range: 1--19). Edges extending
from MLHs displayed to other MCGs are not shown.}\label{biggraph}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=0.61000\textwidth]{../../results/figures/publication/Figure7Z.pdf}
\caption{Biplot showing five most influential explanatory variables
(arrows) overlayed on the first two eigenvectors of distance based
redundancy analysis of \emph{Sclerotinia sclerotiorum} isolates. The
length of the arrows are directly proportional to the strength of the
correlation between explanatory and molecular variables. Open circles
represent the 318 clone-corrected haplotypes in ordination
space.}\label{rda-biplot}
\end{figure}

\begin{figure}
\centering
\includegraphics{../../results/figures/publication/aggressiveness.pdf}
\caption{Strip Plot of aggressiveness by population arranged in
descending order of mean aggressiveness for all populations with N
\textgreater{} 5. White bars represent mean value. Circles represent
individual isolates where filled circles are isolates from white mold
screening nurseries (wmn) and open circles are isolates from producer
fields.}\label{aggressiveness-boxplot}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=0.61000\textwidth]{../../results/figures/publication/mlg-11.pdf}
\caption{Network of populations (nodes/circles) and their shared
multilocus haplotypes (MLH) (edges/lines) genotyped over 11 loci. Each
node is labeled with \textbf{name (number of MLHs shared/number of MLHs
total).} The shade and area of the nodes are proportional to the number
of unique MLHs within the node and the inner nodes are proportional to
the number of private MLHs to the region (bottom legend). Each edge
represents a single MLH where its thickness represents the number of
populations that share the MLH and the shade represents the value of
\(P_{sex}\), or the probability of encountering that MLH from two
independent meiotic events.}\label{community-graph}
\end{figure}

@@

\begin{longtable}[]{@{}lrrrrr@{}}
\caption{\label{tab:amova} Comparison of populations in the white mold
screening nurseries (wmn) and producer fields using an analysis of
molecular variance on Bruvo's genetic distance showing no apparent
differentiation between wmn and other sources. The hierarchy was
constructed as Source/Region where source is defined as belonging to a
wmn or producer field. Bold \(\Phi\) values indicate significant
difference (\emph{P} \textless{} 0.05). S.S. = Sum of Squares, d.f. =
degrees of freedom.}\tabularnewline
\toprule
\begin{minipage}[b]{0.31\columnwidth}\raggedright\strut
Hierarchy\strut
\end{minipage} & \begin{minipage}[b]{0.06\columnwidth}\raggedleft\strut
d.f.\strut
\end{minipage} & \begin{minipage}[b]{0.06\columnwidth}\raggedleft\strut
S.S.\strut
\end{minipage} & \begin{minipage}[b]{0.14\columnwidth}\raggedleft\strut
\% variation\strut
\end{minipage} & \begin{minipage}[b]{0.19\columnwidth}\raggedleft\strut
\(\Phi\) statistic\strut
\end{minipage} & \begin{minipage}[b]{0.05\columnwidth}\raggedleft\strut
\emph{P}\strut
\end{minipage}\tabularnewline
\midrule
\endfirsthead
\toprule
\begin{minipage}[b]{0.31\columnwidth}\raggedright\strut
Hierarchy\strut
\end{minipage} & \begin{minipage}[b]{0.06\columnwidth}\raggedleft\strut
d.f.\strut
\end{minipage} & \begin{minipage}[b]{0.06\columnwidth}\raggedleft\strut
S.S.\strut
\end{minipage} & \begin{minipage}[b]{0.14\columnwidth}\raggedleft\strut
\% variation\strut
\end{minipage} & \begin{minipage}[b]{0.19\columnwidth}\raggedleft\strut
\(\Phi\) statistic\strut
\end{minipage} & \begin{minipage}[b]{0.05\columnwidth}\raggedleft\strut
\emph{P}\strut
\end{minipage}\tabularnewline
\midrule
\endhead
\begin{minipage}[t]{0.31\columnwidth}\raggedright\strut
Between Region\strut
\end{minipage} & \begin{minipage}[t]{0.06\columnwidth}\raggedleft\strut
13\strut
\end{minipage} & \begin{minipage}[t]{0.06\columnwidth}\raggedleft\strut
10.19\strut
\end{minipage} & \begin{minipage}[t]{0.14\columnwidth}\raggedleft\strut
8.45\strut
\end{minipage} & \begin{minipage}[t]{0.19\columnwidth}\raggedleft\strut
\textbf{0.0845}\strut
\end{minipage} & \begin{minipage}[t]{0.05\columnwidth}\raggedleft\strut
0.032\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.31\columnwidth}\raggedright\strut
Between Source within Region\strut
\end{minipage} & \begin{minipage}[t]{0.06\columnwidth}\raggedleft\strut
8\strut
\end{minipage} & \begin{minipage}[t]{0.06\columnwidth}\raggedleft\strut
2.74\strut
\end{minipage} & \begin{minipage}[t]{0.14\columnwidth}\raggedleft\strut
-2.29\strut
\end{minipage} & \begin{minipage}[t]{0.19\columnwidth}\raggedleft\strut
-0.0250\strut
\end{minipage} & \begin{minipage}[t]{0.05\columnwidth}\raggedleft\strut
0.498\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.31\columnwidth}\raggedright\strut
Between Year within Source\strut
\end{minipage} & \begin{minipage}[t]{0.06\columnwidth}\raggedleft\strut
22\strut
\end{minipage} & \begin{minipage}[t]{0.06\columnwidth}\raggedleft\strut
9.37\strut
\end{minipage} & \begin{minipage}[t]{0.14\columnwidth}\raggedleft\strut
16.28\strut
\end{minipage} & \begin{minipage}[t]{0.19\columnwidth}\raggedleft\strut
\textbf{0.173}\strut
\end{minipage} & \begin{minipage}[t]{0.05\columnwidth}\raggedleft\strut
0.001\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.31\columnwidth}\raggedright\strut
Within Year\strut
\end{minipage} & \begin{minipage}[t]{0.06\columnwidth}\raggedleft\strut
274\strut
\end{minipage} & \begin{minipage}[t]{0.06\columnwidth}\raggedleft\strut
47.30\strut
\end{minipage} & \begin{minipage}[t]{0.14\columnwidth}\raggedleft\strut
77.56\strut
\end{minipage} & \begin{minipage}[t]{0.19\columnwidth}\raggedleft\strut
\textbf{0.224}\strut
\end{minipage} & \begin{minipage}[t]{0.05\columnwidth}\raggedleft\strut
0.001\strut
\end{minipage}\tabularnewline
\bottomrule
\end{longtable}

@@

Discriminant Analysis of Principal Components (DAPC) was performed
grouping by Region with the first 20 principal components, representing
87.1\% of the total variance. The first discriminant axis (representing
35\% of the discriminatory power) separated the centroid for the Mexico
isolates from the rest of the data, indicating strong differentiation
(Fig. \ref{DAPC}b). The second discriminant axis, representing 24.1\% of
the discriminatory power, separated the centroid for the CA isolates.
The mean population assignment probabilities for all populations with n
\textgreater{} 10 showed that only isolates from Mexico, CA, and France
had \textgreater{} 50\% probabilities of being reassigned to their
source populations (Fig. \ref{DAPC}a).

@@

\begin{figure}
\centering
\includegraphics[width=1.00000\textwidth]{../../results/figures/publication/DAPC.pdf}
\caption{Discriminant Analysis of Principal Components on regions
showing that Mexico is differentiated from other populations.
\textbf{A)} Scatter plot of first two components from DAPC. Points
represent observed individuals connected to the population centroids
with ellipses representing a 66\% confidence interval for a normal
distribution. The center of each component is represented as black grid
lines. \textbf{B)} Mean population assignment probability from the DAPC
for all populations with N \textgreater{} 10 (facets). Populations
represented along the horizontal axis and probability of assignment on
the vertical. Numbers next to source populations indicate population
size. All values sum to one.}\label{DAPC}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.61000\textwidth]{../../results/figures/publication/dapc_region_year_micanewa.pdf}
\caption{Scatter plot of Discriminant Analysis of Principal Components
on Regions and Years showing non-differentiated temporal variation NE
and MI and temporal variation in WA and CA. Points (text labels)
represent observed individuals connected to the population centroids
with ellipses representing a 66\% confidence interval for a normal
distribution. The center of each component is represented as black grid
lines. A more detailed view is shown in Fig.
\ref{DAPC-RY-FULL}.}\label{DAPC-RY}
\end{figure}

@@

@@

The authors would like to thank Rebecca Higgens for providing valuable
insights into the historical context of the data collection and
curation. Funding for this research was provided by the North Central
Soybean Research Program (\#639K623) to SEE, a Layman Award (\#2446) to
SEE, USDA-ARS National Sclerotinia Initiative (\#58-5442-2-209) to
JRS/SEE, and start-up funds from the University of Nebraska-Lincoln to
SEE.

@@

\begin{figure}
\centering
\includegraphics[width=1.00000\textwidth]{../../results/figures/publication/full-graph.pdf}
\caption{Graph showing complex associations between Mycelial
Compatibility Groups (MCG) (dotted nodes) and Multilocus Haplotypes
(MLH) (full nodes) where the number in each node represents the MLH/MCG
assignment. Node size reflect the number of samples represented by each
node (circle). Edges (arrows) point from MLH to MCG where the weight
(thickness) of the edge represents the number of samples shared. Node
color represents the community assignment based on the walktrap
algorithm with a maximum of four steps (Pons \& Latapy,
2006).}\label{fullgraph}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=1.00000\textwidth]{../../results/figures/publication/mlg-16.pdf}
\caption{Network of populations (nodes/circles) and their shared
multilocus haplotypes (MLH) (edges/lines) haplotyped over 16 loci. Each
node is labeled with \textbf{name (number of MLHs shared/number of MLHs
total).} The shade and area of the nodes are proportional to the number
of unique MLHs within the node and the inner nodes are proportional to
the number of private MLHs to the region (bottom legend). Each edge
represents a single MLH where its thickness represents the number of
populations that share the MLH and the shade represents the value of
\(P_{sex}\), or the probability of encountering that MLH from two
independent meiotic events.}\label{community-graph16}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=1.00000\textwidth]{../../results/figures/publication/dapc_region_year.pdf}
\caption{Scatter plot of Discriminant Analysis of Principal Components
on Regions and Years showing temporal variation across all Regions.
Points (text labels) represent observed individuals connected to the
population centroids with ellipses representing a 66\% confidence
interval for a normal distribution. The center of each component is
represented as black grid lines.}\label{DAPC-RY-FULL}
\end{figure}

@@

\hypertarget{ref-leslie1993fungal}{}
Leslie, J. (1993). Fungal vegetative compatibility. \emph{Annual Review
of Phytopathology}, \emph{31}, 127--150. Review.
\url{https://doi.org/10.1146/annurev.py.31.090193.001015}

>>>>

\begin{figure}[htbp]
\centering
\includegraphics[width=1.00000\textwidth]{../../results/figures/publication/mcg-subgraph-with-context.pdf}
\caption{Associations between Mycelial Compatibility Groups and
Multilocus Haplotypes. \textbf{A)} Barplot of Mycelial Compatibility
Group (MCG) abundance in descending order. Singletons (46) were
truncated, leaving 41 MCGs. White bars represent sample counts and grey
bars represent counts of unique multilocus haplotypes (MLH). The
transparency of the bars represent the evenness of the distribution of
the MLHs within a given MCG. A dashed box surrounds the eight most
common MCGs representing \textgreater{}~51\% of the data. \textbf{B)}
Full graph-representation of the relationship between MCGs (open
circles) and MLHs (filled circles). Details in Fig. \ref{fullgraph}.
\textbf{C)} A subset of \textbf{B} representing the 8 most common MCGs
and their associated MLHs (dashed box in \textbf{A}). Filled nodes
(circles) represent MLHs and open nodes represent MCGs. Node area scaled
to the number of samples represented (range: 1--73). Numbers inside
nodes are the MLH/MCG label (if n \textgreater{} 1). Edges (arrows)
point from MLH to MCG where the weight (thickness) of the edge
represents the number of shared isolates (range: 1--19). Edges extending
from MLHs displayed to other MCGs are not shown.}\label{biggraph}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\includegraphics[width=0.61000\textwidth]{../../results/figures/publication/Figure7Z.pdf}
\caption{Biplot showing five most influential explanatory variables
(arrows) overlayed on the first two eigenvectors of distance based
redundancy analysis of \emph{Sclerotinia sclerotiorum} isolates. The
length of the arrows are directly proportional to the strength of the
correlation between explanatory and molecular variables. Open circles
represent the 318 clone-corrected haplotypes in ordination
space.}\label{rda-biplot}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics{../../results/figures/publication/aggressiveness.pdf}
\caption{Strip Plot of aggressiveness by population arranged in
descending order of mean aggressiveness for all populations with N
\textgreater{} 5. White bars represent mean value. Circles represent
individual isolates where filled circles are isolates from white mold
screening nurseries (wmn) and open circles are isolates from producer
fields.}\label{aggressiveness-boxplot}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\includegraphics[width=0.61000\textwidth]{../../results/figures/publication/mlg-11.pdf}
\caption{Network of populations (nodes/circles) and their shared
multilocus haplotypes (MLH) (edges/lines) genotyped over 11 loci. Each
node is labeled with \textbf{name (number of MLHs shared/number of MLHs
total).} The shade and area of the nodes are proportional to the number
of unique MLHs within the node and the inner nodes are proportional to
the number of private MLHs to the region (bottom legend). Each edge
represents a single MLH where its thickness represents the number of
populations that share the MLH and the shade represents the value of
\(P_{sex}\), or the probability of encountering that MLH from two
independent meiotic events.}\label{community-graph}
\end{figure}

@@

\begin{longtable}[]{@{}lrrrrr@{}}
\caption{\label{tab:amova} Comparison of populations in the white mold
screening nurseries (wmn) and producer fields using an analysis of
molecular variance on Bruvo's genetic distance showing no apparent
differentiation between wmn and other sources. The hierarchy was
constructed as Source/Region where source is defined as belonging to a
wmn or producer field. Bold \(\Phi\) values indicate significant
difference (\emph{P} \textless{} 0.05). S.S. = Sum of Squares, d.f. =
degrees of freedom.}\tabularnewline
\toprule
\begin{minipage}[b]{0.31\columnwidth}\raggedright\strut
Hierarchy\strut
\end{minipage} & \begin{minipage}[b]{0.06\columnwidth}\raggedleft\strut
d.f.\strut
\end{minipage} & \begin{minipage}[b]{0.06\columnwidth}\raggedleft\strut
S.S.\strut
\end{minipage} & \begin{minipage}[b]{0.14\columnwidth}\raggedleft\strut
\% variation\strut
\end{minipage} & \begin{minipage}[b]{0.19\columnwidth}\raggedleft\strut
\(\Phi\) statistic\strut
\end{minipage} & \begin{minipage}[b]{0.05\columnwidth}\raggedleft\strut
\emph{P}\strut
\end{minipage}\tabularnewline
\midrule
\endfirsthead
\toprule
\begin{minipage}[b]{0.31\columnwidth}\raggedright\strut
Hierarchy\strut
\end{minipage} & \begin{minipage}[b]{0.06\columnwidth}\raggedleft\strut
d.f.\strut
\end{minipage} & \begin{minipage}[b]{0.06\columnwidth}\raggedleft\strut
S.S.\strut
\end{minipage} & \begin{minipage}[b]{0.14\columnwidth}\raggedleft\strut
\% variation\strut
\end{minipage} & \begin{minipage}[b]{0.19\columnwidth}\raggedleft\strut
\(\Phi\) statistic\strut
\end{minipage} & \begin{minipage}[b]{0.05\columnwidth}\raggedleft\strut
\emph{P}\strut
\end{minipage}\tabularnewline
\midrule
\endhead
\begin{minipage}[t]{0.31\columnwidth}\raggedright\strut
Between Region\strut
\end{minipage} & \begin{minipage}[t]{0.06\columnwidth}\raggedleft\strut
13\strut
\end{minipage} & \begin{minipage}[t]{0.06\columnwidth}\raggedleft\strut
10.19\strut
\end{minipage} & \begin{minipage}[t]{0.14\columnwidth}\raggedleft\strut
8.45\strut
\end{minipage} & \begin{minipage}[t]{0.19\columnwidth}\raggedleft\strut
\textbf{0.0845}\strut
\end{minipage} & \begin{minipage}[t]{0.05\columnwidth}\raggedleft\strut
0.029\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.31\columnwidth}\raggedright\strut
Between Source within Region\strut
\end{minipage} & \begin{minipage}[t]{0.06\columnwidth}\raggedleft\strut
8\strut
\end{minipage} & \begin{minipage}[t]{0.06\columnwidth}\raggedleft\strut
2.74\strut
\end{minipage} & \begin{minipage}[t]{0.14\columnwidth}\raggedleft\strut
-2.29\strut
\end{minipage} & \begin{minipage}[t]{0.19\columnwidth}\raggedleft\strut
-0.0250\strut
\end{minipage} & \begin{minipage}[t]{0.05\columnwidth}\raggedleft\strut
0.486\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.31\columnwidth}\raggedright\strut
Between Year within Source\strut
\end{minipage} & \begin{minipage}[t]{0.06\columnwidth}\raggedleft\strut
22\strut
\end{minipage} & \begin{minipage}[t]{0.06\columnwidth}\raggedleft\strut
9.37\strut
\end{minipage} & \begin{minipage}[t]{0.14\columnwidth}\raggedleft\strut
16.28\strut
\end{minipage} & \begin{minipage}[t]{0.19\columnwidth}\raggedleft\strut
\textbf{0.173}\strut
\end{minipage} & \begin{minipage}[t]{0.05\columnwidth}\raggedleft\strut
0.001\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.31\columnwidth}\raggedright\strut
Within Year\strut
\end{minipage} & \begin{minipage}[t]{0.06\columnwidth}\raggedleft\strut
274\strut
\end{minipage} & \begin{minipage}[t]{0.06\columnwidth}\raggedleft\strut
47.30\strut
\end{minipage} & \begin{minipage}[t]{0.14\columnwidth}\raggedleft\strut
77.56\strut
\end{minipage} & \begin{minipage}[t]{0.19\columnwidth}\raggedleft\strut
\textbf{0.224}\strut
\end{minipage} & \begin{minipage}[t]{0.05\columnwidth}\raggedleft\strut
0.001\strut
\end{minipage}\tabularnewline
\bottomrule
\end{longtable}

@@

Discriminant Analysis of Principal Components (DAPC) was performed
grouping by Region with the first 21 principal components, representing
88.1\% of the total variance. The first discriminant axis (representing
36.1\% of the discriminatory power) separated the centroid for the
Mexico isolates from the rest of the data, indicating strong
differentiation (Fig. \ref{DAPC}b). The second discriminant axis,
representing 25.3\% of the discriminatory power, separated the centroid
for the CA isolates. The mean population assignment probabilities for
all populations with n \textgreater{} 10 showed that only isolates from
Mexico, CA, and France had \textgreater{} 50\% probabilities of being
reassigned to their source populations (Fig. \ref{DAPC}a).

@@

\begin{figure}[htbp]
\centering
\includegraphics[width=1.00000\textwidth]{../../results/figures/publication/DAPC.pdf}
\caption{Discriminant Analysis of Principal Components on regions
showing that Mexico is differentiated from other populations.
\textbf{A)} Scatter plot of first two components from DAPC. Points
represent observed individuals connected to the population centroids
with ellipses representing a 66\% confidence interval for a normal
distribution. The center of each component is represented as black grid
lines. \textbf{B)} Mean population assignment probability from the DAPC
for all populations with N \textgreater{} 10 (facets). Populations
represented along the horizontal axis and probability of assignment on
the vertical. Numbers next to source populations indicate population
size. All values sum to one.}\label{DAPC}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics[width=0.61000\textwidth]{../../results/figures/publication/dapc_region_year_micanewa.pdf}
\caption{Scatter plot of Discriminant Analysis of Principal Components
on Regions and Years showing non-differentiated temporal variation NE
and MI and temporal variation in WA and CA. Points (text labels)
represent observed individuals connected to the population centroids
with ellipses representing a 66\% confidence interval for a normal
distribution. The center of each component is represented as black grid
lines. A more detailed view is shown in Fig.
\ref{DAPC-RY-FULL}.}\label{DAPC-RY}
\end{figure}

@@

\subsection*{Funding}\label{funding}
\addcontentsline{toc}{subsection}{Funding}

Funding for this research was provided by the North Central Soybean
Research Program (\#639K623) to SEE, a Layman Award (\#2446) to SEE,
USDA-ARS National Sclerotinia Initiative (\#58-5442-2-209) to JRS/SEE,
and start-up funds from the University of Nebraska-Lincoln to SEE. The
funders had no role in study design, data collection and analysis,
decision to publish, or preparation of the manuscript.

@@

The authors would like to thank Rebecca Higgens for providing valuable
insights into the historical context of the data collection and
curation.

@@

\begin{figure}[htbp]
\centering
\includegraphics[width=1.00000\textwidth]{../../results/figures/publication/full-graph.pdf}
\caption{Graph showing complex associations between Mycelial
Compatibility Groups (MCG) (dotted nodes) and Multilocus Haplotypes
(MLH) (full nodes) where the number in each node represents the MLH/MCG
assignment. Node size reflect the number of samples represented by each
node (circle). Edges (arrows) point from MLH to MCG where the weight
(thickness) of the edge represents the number of samples shared. Node
color represents the community assignment based on the walktrap
algorithm with a maximum of four steps (Pons \& Latapy,
2006).}\label{fullgraph}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics[width=1.00000\textwidth]{../../results/figures/publication/mlg-16.pdf}
\caption{Network of populations (nodes/circles) and their shared
multilocus haplotypes (MLH) (edges/lines) haplotyped over 16 loci. Each
node is labeled with \textbf{name (number of MLHs shared/number of MLHs
total).} The shade and area of the nodes are proportional to the number
of unique MLHs within the node and the inner nodes are proportional to
the number of private MLHs to the region (bottom legend). Each edge
represents a single MLH where its thickness represents the number of
populations that share the MLH and the shade represents the value of
\(P_{sex}\), or the probability of encountering that MLH from two
independent meiotic events.}\label{community-graph16}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics[width=1.00000\textwidth]{../../results/figures/publication/dapc_region_year.pdf}
\caption{Scatter plot of Discriminant Analysis of Principal Components
on Regions and Years showing temporal variation across all Regions.
Points (text labels) represent observed individuals connected to the
population centroids with ellipses representing a 66\% confidence
interval for a normal distribution. The center of each component is
represented as black grid lines.}\label{DAPC-RY-FULL}
\end{figure}

@@

\hypertarget{ref-leslie1993fungal}{}
Leslie, J. (1993). Fungal vegetative compatibility. \emph{Annual Review
Of Phytopathology}, \emph{31}, 127--150. Review.
\url{https://doi.org/10.1146/annurev.py.31.090193.001015}
